Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-17 manuscript.tex
2.3

%: rhythms as a 
The idea of using the synchrony of coactivation in a cell assembly is an hypothesis that was formalized by~\citet{hebb_organization_1949}. 
This is also expressed in the idea that different cortical areas could achieve binding by synchrony~\citep{fries_mechanism_2005}. The synchronicity will generate rhythms at different range of frequencies with spikes arriving at peak susceptibility (top of a cycle) or down. Such a thory has surprising ly been validated in EEG recordings for example to explain the continuous wagon wheel illusion which corresponds to the pervceived reversal of the rotational movements of the spikes in a rotating wheel~\citep{vanrullen_continuous_2006}. More generallly, it can be shown that the phase of alpha (about $10$ Hz) oscillations  is causally linked with modulations of cortical excitability and with visual perception~\citep{dugue_phase_2011}. 
%
\subsection{A further hypothesis: traveling waves}
%: >>>>>>>> Laurent is here <<<<<<<<<<<<<<
To further investigate the role of precise timing, let us also focus on the role of differential timings in an assembly of neurons. As we have seen, a visual feature will induce the firing of different cells at different latencies~\citep{celebrini_dynamics_1993}. Using intra-cellular recordings, it was shown that the response to a focal visual activation would elicit a latency basin, that is a graded onset of the neural response from the most activated to neighboring neurons~\citep{bringuier_horizontal_1999}. In particular, it was shown that the network of horizontal connections within a cortical area is typically not myelinated and that this latency basin would be determined by the propagation speed within the area. For generic visual scenes, this processes would generate a complex interplay between the dynamics of the sensory signal and the spatio- temporal determinants of these interactions and may underly anticipatory mechanisms in the primary visual cortex~\citep{benvenuti_anticipatory_2020,le_bec_horizontal_2022}.
%
Statistical dependencies in the responses of sensory neurons govern both the amount of stimulus information conveyed and the means by which downstream neurons can extract it. This is put in evidence by analysing the functional significance of correlated firing in a complete population of macaque parasol retinal ganglion cells using a model of multi-neuron spike responses~\citep{pillow_spatio-temporal_2008}. This show precise spatio-temporal differences in this recurrently connected assembly. The different aspects of information in the data are evaluated by a decoding strategy highlighting the role of correlations. A similar dataset used in~\citep{schneidman_weak_2006} is available from M. Berry's lab~\citep{berry_spike_2022}.

@@

Interestingly, it can be shown that these travelling waves could have a measurable role on theactivity of the visual cortex. This has been illustrated in a recent study studying the long-range apparent motion effect (lrAM)~\citep{chemla_suppressive_2019}. The lrAM is the simple effect of perceiving a smooth motion when showing two dots in a temporal sequence and in close visual proximity. The lrAM is the building block of the use of sequences of images to induce the perception of smooth, realistic visual scenes which is at the base of movies seen in cinema theaters. In this study, authors used voltage-sensitive dye imaging to record the activty of the primary visual cortex of macaque monkeys to the presentation of the dots alone or in conjunction. A probabilistic modelling has shown that the activity of the joint presentation induced a suppressive wave in the direction opposed to the perceived direction, shaping the formation of a wave of propagation travelling at a speed compatible with the perceived motion. A computational model validated the hypothesis that this process could be mediated by diffusion in the horizontal layers connecting the differnt locations within this cortical area.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A novel hypothesis: precise spiking motifs in cell assemblies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

~\citep{bienenstock_model_1995} : from synfire chains to Synfire braids

A notable exception is the polychronization model of Izhikevich~\citep{izhikevich_polychronization_2006}, which combined the construction of a random recurrent model of spiking neurons including such delays and whose weights evolved with a Spike-Time Dependent Plasticity (STDP) learning rule. In this model, raster plot analysis showed repeated activation of Polychronous Groups (PGs), i.e., specific spike patterns with a specific sequence of activations.

In neuronal models, an efficient use or detection of these spatio-temporal patterns embedded in the spike train comes with the integration of heterogeneous delays~\citep{guise_bayesian_2014,zhang_supervised_2020}. Notably, Izhikevich~\citep{izhikevich_polychronization_2006} introduced the notion of polychronous groups (PGs) as a repetitive motif of spikes defined by a subset of neurons with different, yet precise, spiking delays. This representation has a much greater information capacity in comparison to other neural coding approaches through their connectivity and the possible coexistence of numerous superposed PGs.

%
Currently, there is a consensus for rate-based coding models in computational and biological neuroscience. Nevertheless, there is a substantial literature in neurobiology indicating that brain dynamics often organize into stereotyped sequences (like synfire chains~\citep{ikegaya_synfire_2004}, packets~\citep{luczak_sequential_2007} or hippocampal sequences~\citep{pastalkova_internally_2008,villette_internally_2015} and on the role of such precise spike timing in downstream information transfer and coding~\citep{villette_internally_2015,branco_dendritic_2010,luczak_packet-based_2015}. This is for instance relevant in sensory pathways in vision~\citep{meister_concerted_1995}, audition~\citep{decharms_primary_1996}, olfaction~\citep{wehr_odour_1996} or touch~\citep{johansson_first_2004}. In particular, one theoretical viewpoint considers synfire braids (Bienenstock, 1995), where a precise sequential motif of spikes will synchronize as it reaches the soma of a neuron for which synaptic delays are adequately tuned. In particular, computational modeling shows that at the scale of neurons, an efficient neural code can emerge where spike times are organized in prototypical, precise temporal motifs (Izhikevich, 2006) which he defined as polychronous groups.

Stereotyped sequences of neural activation have been particularly well described in the adult hippocampus and related to its function in mental travel in time and space~\citep{buzsaki_space_2018}. These sequences can be internally generated~\citep{pastalkova_internally_2008,villette_internally_2015} and are formed by the chained activation of orthogonal assemblies, themselves organized as sequence packets (Malvache et al., 2016). Thus, hippocampal sequences are formed by the ordered activation of smaller sequence motifs. They are stereotyped and robust, since neurons can be activated in the same order across days (see Figure
~\ref{fig:haimerl} from~\citep{haimerl_internal_2019} below). As a consequence, hippocampal sequences may rely on an internally hardwired structure and form the functional building blocks for encoding, storing and retrieving experience.

Such observations suggest that neural groups or ensembles, rather than individual neurons, are emergent functional units of cortical activity~\citep{miller_visual_2014}. This work shows, using two-photon calcium imaging of populations of neurons from the primary visual cortex of awake mice during visual stimulation and spontaneous activity, that whereas intrinsic ensembles recur at random time intervals, visually evoked ensembles are time-locked to stimuli. It proposes that visual stimuli recruit endogenously generated ensembles to represent visual attributes. Note that evoked ensembles in response to a natural movie played in a loop were precisely timed across repetitions (Fig. 7).
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Precisely timing motifs in neuromorphic engineering}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A natural candidate to use these precise temporal patterns in the brain is to use Spiking Neural Networks (SNNs)~\citep{maass_networks_1997}. The approach which is at present most prominent in the SNNs community is to use existing algorithms from machine learning and to adapt them to the specificity of spiking architectures. One such example is to adapt the successes of deep learning algorithms and to transfer the back-propagation algorithm to SNNs, for instance with a surrogate gradient. This approach is quite successful, and SNNs approach in some case the performance of Deep Learning algorithms, for instance on the N-MNIST dataset for categorizing digits in a stream of events. However, most biological neural systems use spikes and are obviously more efficient than current state-of-the-art vision systems, both in terms of efficiency (accuracy), in speed (latency), and energy consumption. There is therefore an immense gap in the way we understand biology to translate it to the efficiency of SNNs. Our approach will be to focus on the temporal representation of information directly. In particular, our objective is to fully exploit the capacity of spiking neurons to detect synchronous patterns.

\textbf{TODO: a paragraph on our existing work}
Our approach would be distinct than these approaches from us and colleagues as we will directly deal with delays in the system at the presynaptic level.

@@

\begin{itemize}
\item
  A crucial advantage of Spiking Neural Networks (SNNs) architectures lies in its processing of temporal information. Yet, most SNNs encode the temporal signal as an analog signal and try to ``cross-compile'' classical Neural Network to a spiking architecture. To go beyond the state-of-the-art, we will review here on one core computation of a spiking neuron, that is, is its ability to switch from the classical integrator mode (summing analog currents on its synapses) to a synchrony detector where it emits a spike whenever presynaptic spiking inputs are synchronized. To overcome the diversity of input presynaptic patterns, we will explore different existing architectures to learn to detect stable ``polychronous`` events, that is, volleys of spikes which are stable up to certain synaptic delays. These models will be compared in light of neuroscientific and computational perspectives. We review theoretical and computational foundations of PG detection in models.
\item
  Application to Image processing using sparse spiking representations: Using the core computational unit defined, extension of the computation to a topographic representation similar to that observed in the primary visual cortex of mammals. design of micro-circuits with specific lateral interactions will allow us to design efficient micro-circuits for the sparse representation of images.
\end{itemize}

Finally we will discuss future avenues for effective PG detection and learning in event streams.

%%

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Models for the detection of precise spiking motifs}\label{sec:detection}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the following of this section, we will review theoretical models which directly tackle the problem of using precise spiking motifs.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In computational neuroscience: Izhikevitch's polychronization model}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Neurobiology spike distances}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{decoding neural activity/ spike distances}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Learning to detect polychronous groups}\label{learning-to-detect-polychronous-groups}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Learning weights \ldots{} and delays}\label{learning-weights-and-delays}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
spike time coding in a neuron: We will describe the Spike-Time Dependent Plasticity (STDP)~\citep{markram_regulation_1997} rule which implement an unsupervised learning aiming at optimizing the detection of polychronous patterns, that is volleys of spikes which are synchronized, up to some stable pattern of pre-synaptic delays. This STDP rule will be based by the inversion of the generative model for spike formation and will therefore be derived by a Bayesian approach. This will decouple the active synapses (similarly to a logistic regression) from the values of possible synaptic delays.

>>>>

%: rhythms as a 
The idea of using the synchrony of coactivation in a cell assembly is an hypothesis that was formalized by~\citet{hebb_organization_1949}. 
This is also expressed in the idea that different cortical areas could achieve binding by synchrony~\citep{fries_mechanism_2005}. The synchronicity will generate rhythms at different range of frequencies with spikes arriving at peak susceptibility (top of a cycle) or down. Such a thory has surprising ly been validated in EEG recordings for example to explain the continuous wagon wheel illusion which corresponds to the pervceived reversal of the rotational movements of the spikes in a rotating wheel~\citep{vanrullen_continuous_2006}. More generallly, it can be shown that the phase of alpha (about $10$ Hz) oscillations  is causally linked with modulations of cortical excitability and with visual perception~\citep{dugue_phase_2011}. 
%
\subsection{A further hypothesis: traveling waves}
To further investigate the role of precise timing, let us also focus on the role of differential timings in an assembly of neurons. As we have seen, a visual feature will induce the firing of different cells at different latencies~\citep{celebrini_dynamics_1993}. Using intra-cellular recordings, it was shown that the response to a focal visual activation would elicit a latency basin, that is a graded onset of the neural response from the most activated to neighboring neurons~\citep{bringuier_horizontal_1999}. In particular, it was shown that the network of horizontal connections within a cortical area is typically not myelinated and that this latency basin would be determined by the propagation speed within the area. For generic visual scenes, this processes would generate a complex interplay between the dynamics of the sensory signal and the spatio- temporal determinants of these interactions and may underly anticipatory mechanisms in the primary visual cortex~\citep{benvenuti_anticipatory_2020,le_bec_horizontal_2022}.
%

@@

Interestingly, it can be shown that these travelling waves could have a measurable role on theactivity of the visual cortex. This has been illustrated in a recent study studying the long-range apparent motion effect (lrAM)~\citep{chemla_suppressive_2019}. The lrAM is the simple effect of perceiving a smooth motion when showing two dots in a temporal sequence and in close visual proximity. The lrAM is the building block of the use of sequences of images to induce the perception of smooth, realistic visual scenes which is at the base of movies seen in cinema theaters. In this study, authors used voltage-sensitive dye imaging to record the activty of the primary visual cortex of macaque monkeys to the presentation of the dots alone or in conjunction. A probabilistic modelling has shown that the activity of the joint presentation induced a suppressive wave in the direction opposed to the perceived direction, shaping the formation of a wave of propagation travelling at a speed compatible with the perceived motion. A computational model validated the hypothesis that this process could be mediated by diffusion in the horizontal layers connecting the differnt locations within this cortical area.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A novel hypothesis: precise spiking motifs in cell assemblies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Travelling waves indicate that spatio-temporal correlations could play an important role in shaping neural activity. For instance, statistical dependencies in the responses of sensory neurons govern both the amount of stimulus information conveyed and the means by which downstream neurons can extract it. In particular, this was put in evidence by analysing the functional significance of correlated firing in a complete population of macaque parasol retinal ganglion cells using a model of multi-neuron spike responses~\citep{pillow_spatio-temporal_2008}. This shows precise spatio-temporal differences in this recurrently connected assembly. The different aspects of information in the data are evaluated by a decoding strategy highlighting the role of correlations. Note that a similar dataset used in~\citep{schneidman_weak_2006} is available from M. Berry's lab~\citep{berry_spike_2022} and allows to perform and validate thiese hypothesis. However a limit of explaining such data with traveling waves is that in theory a traveling wave would be stationaryn, which is incomptaible with the limits (in space and time) of a neural system.

Moreover, there is a consensus for rate-based coding models in computational and biological neuroscience. Nevertheless, there is a substantial literature in neurobiology indicating that brain dynamics often organize into stereotyped sequences (like synfire chains~\citep{ikegaya_synfire_2004}, packets~\citep{luczak_sequential_2007} or hippocampal sequences~\citep{pastalkova_internally_2008,villette_internally_2015} and on the role of such precise spike timing in downstream information transfer and coding~\citep{villette_internally_2015,branco_dendritic_2010,luczak_packet-based_2015}. This is for instance relevant in sensory pathways in vision~\citep{meister_concerted_1995}, audition~\citep{decharms_primary_1996}, olfaction~\citep{wehr_odour_1996} or touch~\citep{johansson_first_2004}. In particular, one theoretical viewpoint considers synfire braids~\citep{bienenstock_model_1995}, where a precise sequential motif of spikes will synchronize as it reaches the soma of a neuron for which synaptic delays are adequately tuned. In particular, computational modeling shows that at the scale of neurons, an efficient neural code can emerge where spike times are organized in prototypical, precise temporal motifs~\citep{izhikevich_polychronization_2006} which he defined as \emph{polychronous groups}.

Stereotyped sequences of neural activation have been particularly well described in the adult hippocampus and related to its function in mental travel in time and space~\citep{buzsaki_space_2018}. These sequences can be internally generated~\citep{pastalkova_internally_2008,villette_internally_2015} and are formed by the chained activation of orthogonal assemblies, themselves organized as sequence packets~\citep{malvache_awake_2016}. Thus, hippocampal sequences are formed by the ordered activation of smaller sequence motifs. They are stereotyped and robust, since neurons can be activated in the same order across days (see Figure
~\ref{fig:haimerl} from~\citep{haimerl_internal_2019} below). As a consequence, hippocampal sequences may rely on an internally hardwired structure and form the functional building blocks for encoding, storing and retrieving experience.
The rest of this review will be devoted to present evidence for the use of precise spiking motifs in computational neuroscience, neurobiology and neuromorphic engineering.

%: >>>>>>>> Laurent is here <<<<<<<<<<<<<<

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Precisely timing motifs in computational neuroscience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the following section, we will review theoretical models which directly tackle the problem of using precise spiking motifs. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A natural candidate to use these precise temporal patterns in the brain is to use Spiking Neural Networks (SNNs)~\citep{maass_networks_1997}. The approach which is at present most prominent in the SNNs community is to use existing algorithms from machine learning and to adapt them to the specificity of spiking architectures. One such example is to adapt the successes of deep learning algorithms and to transfer the back-propagation algorithm to SNNs, for instance with a surrogate gradient and try to ``cross-compile'' classical Neural Network to a spiking architecture. This approach is quite successful, and SNNs approach in some case the performance of Deep Learning algorithms, for instance on the N-MNIST dataset for categorizing digits in a stream of events. However, most biological neural systems use spikes and are obviously more efficient than current state-of-the-art vision systems, both in terms of efficiency (accuracy), in speed (latency), and energy consumption. There is therefore an immense gap in the way we understand biology to translate it to the efficiency of SNNs.  To go beyond the state-of-the-art, we will review here on one core computation of a spiking neuron, that is, is its ability to switch from the classical integrator mode (summing analog currents on its synapses) to a synchrony detector where it emits a spike whenever presynaptic spiking inputs are synchronized. To overcome the diversity of input presynaptic patterns, we will explore different existing architectures to learn to detect stable ``polychronous`` events, that is, volleys of spikes which are stable up to certain synaptic delays. These models will be compared in light of neuroscientific and computational perspectives. We review theoretical and computational foundations of PG detection in models. In particular, our objective is to describe methods which fully exploit the capacity of spiking neurons to detect synchronous patterns.

Finally we will discuss future avenues for effective PG detection and learning in event streams.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Izhikevitch's polychronization model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Application to Image processing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Application to Image processing using sparse spiking representations: Using the core computational unit defined, extension of the computation to a topographic representation similar to that observed in the primary visual cortex of mammals. design of micro-circuits with specific lateral interactions will allow us to design efficient micro-circuits for the sparse representation of images.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Precise spiking motifs in neurobiology}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{decoding neural activity/ spike distances}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A notable exception is the polychronization model of Izhikevich~\citep{izhikevich_polychronization_2006}, which combined the construction of a random recurrent model of spiking neurons including such delays and whose weights evolved with a Spike-Time Dependent Plasticity (STDP) learning rule. In this model, raster plot analysis showed repeated activation of Polychronous Groups (PGs), i.e., specific spike patterns with a specific sequence of activations. In neuronal models, an efficient use or detection of these spatio-temporal patterns embedded in the spike train comes with the integration of heterogeneous delays~\citep{guise_bayesian_2014,zhang_supervised_2020}. Notably, Izhikevich~\citep{izhikevich_polychronization_2006} introduced the notion of polychronous groups (PGs) as a repetitive motif of spikes defined by a subset of neurons with different, yet precise, spiking delays. This representation has a much greater information capacity in comparison to other neural coding approaches through their connectivity and the possible coexistence of numerous superposed PGs.

Such observations suggest that neural groups or ensembles, rather than individual neurons, are emergent functional units of cortical activity~\citep{miller_visual_2014}. This work shows, using two-photon calcium imaging of populations of neurons from the primary visual cortex of awake mice during visual stimulation and spontaneous activity, that whereas intrinsic ensembles recur at random time intervals, visually evoked ensembles are time-locked to stimuli. It proposes that visual stimuli recruit endogenously generated ensembles to represent visual attributes. Note that evoked ensembles in response to a natural movie played in a loop were precisely timed across repetitions (Fig. 7).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Precise spiking motifs in  neuromorphic engineering}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Learning weights \ldots{} and delays}\label{learning-weights-and-delays}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
spike time coding in a neuron: We will describe the Spike-Time Dependent Plasticity (STDP)~\citep{markram_regulation_1997} rule which implement an unsupervised learning aiming at optimizing the detection of polychronous patterns, that is volleys of spikes which are synchronized, up to some stable pattern of pre-synaptic delays. This STDP rule will be based by the inversion of the generative model for spike formation and will therefore be derived by a Bayesian approach. This will decouple the active synapses (similarly to a logistic regression) from the values of possible synaptic delays.
